Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-08-22 Supplemental-Material-A-Annotated-Analysis.Rmd
initial stability checks added

```{r testOptimizer05}
cleanM <- function(M, c = 55) {
  check <- list()
  rowNamesOut <- c()
  colNamesOut <- c()
  for (i in 1:length(c(row.names(M), names(M)))) {
    rowMeans <- rowMeans(M) * 100
    colMeans <- colMeans(M) * 100
    rcMeans <- c(rowMeans, colMeans)
    rm <- which.min(rcMeans) %>% names
    rc <- ifelse(startsWith(rm, "PP_"), "row", "col")

@@

### Studies 1-3

We begin by preparing the data for the main analysis. Here, we:

@@

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiMain <- rbind(
  dtS1Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S1") %>% 
    mutate(across(!TID & !study, as.numeric)),
  dtS2Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S2"),
  dtS3Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S3")
) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(IntergroupContact, IngroupContact, na.rm = TRUE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum)
  ) %>%
  ungroup() %>%
  select(ID,
         study,
         date,
         week,
         everything(),
         -PID,
         -starts_with("ResponseId"), 
         -starts_with("roommate"),
         -starts_with("Reason")) %>%
  as.data.frame %>%
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(ID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  mutate(study = replace_na(study, calc_mode(study))) %>%
  ungroup %>%
  group_by(study, TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>%
  as.data.frame

dtMiMainDaily <- rbind(
  dtS1Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S1") %>% 
    mutate(across(!TID & !study, as.numeric)),
  dtS2Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S2"),
  dtS3Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S3")
) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(IntergroupContact, IngroupContact, na.rm = TRUE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum)
  ) %>%
  ungroup() %>%
  group_by(ID, date, study) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>% # contact dum should be summarized as sum()
  ungroup %>%
  group_by(study) %>%
  mutate(TIDnum = as.numeric(factor(date))) %>%
  ungroup %>%
  select(ID,
         study,
         date,
         everything(),
         -PID,
         -starts_with("ResponseId")) %>%
  as.data.frame %>%
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(ID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  mutate(study = replace_na(study, calc_mode(study))) %>%
  ungroup %>%
  group_by(study, TIDnum) %>%
  mutate(across(c("date"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate_if(is.numeric, ~ ifelse(is.nan(.), NA, .)) %>%
  as.data.frame

dtMiMainWeeekly <- rbind(
  dtS1Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S1") %>% 
    mutate(across(!TID & !study, as.numeric)),
  dtS2Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S2"),
  dtS3Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S3")
) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(IntergroupContact, IngroupContact, na.rm = TRUE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum)
  ) %>%
  ungroup() %>%
  group_by(ID, week, study) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup %>%
  group_by(study) %>%
  mutate(TIDnum = as.numeric(factor(week))) %>%
  ungroup %>%
  select(ID,
         study,
         week,
         everything(),
         -PID,
         -starts_with("ResponseId")) %>%
  as.data.frame %>%
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(ID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  mutate(study = replace_na(study, calc_mode(study))) %>%
  ungroup %>%
  group_by(study, TIDnum) %>%
  mutate(across(c("week"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate_if(is.numeric, ~ ifelse(is.nan(.), NA, .)) %>%
  as.data.frame 
```

@@

@@

#################################################################
##               Imputation at Daily Aggregation               ##
#################################################################
# MiMainDaily <-
#   amelia(
#     dtMiMainDaily,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("date", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMainDaily)[!names(dtMiMainDaily) %in% idVars],
#     #lags = names(dtMiMainDaily)[names(dtMiMainDaily) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainDaily)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainDaily))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainDaily, file = "data/imputed/MainDailyImputed.RData")
load("data/imputed/MainDailyImputed.RData")

##################################################################
##               Imputation at Weekly Aggregation               ##
##################################################################
# MiMainWeekly <-
#   amelia(
#     dtMiMainWeeekly,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("week", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMainWeeekly)[!names(dtMiMainWeeekly) %in% idVars],
#     #lags = names(dtMiMainWeeekly)[names(dtMiMainWeeekly) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainWeeekly)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainWeeekly))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainWeekly, file = "data/imputed/MainWeeklyImputed.RData")
load("data/imputed/MainWeeklyImputed.RData")
```

In progress. Weekly might not be possible with all aux variables (i.e., too many variables for too few observations).

@@

dtMiS1Daily <- dtS1Red %>% 
  select(TID, any_of(varNamS1MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(date = as.Date(gsub(" .*", "", TID))) %>%
  group_by(PID, date) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup %>% 
  mutate(TIDnum = as.numeric(factor(date)),
         week = strftime(date, format = "%Y-W%V")) %>% 
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  select(PID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>% # only include variables that vary (i.e., sd != 0)
  as.data.frame

dtMiS1Weekly <- dtS1Red %>% 
  select(TID, any_of(varNamS1MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(date = as.Date(gsub(" .*", "", TID)),
         week = strftime(date, format = "%Y-W%V")) %>%
  group_by(PID, week) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup %>% 
  mutate(TIDnum = as.numeric(factor(week))) %>% 
  select(PID,
         week,
         everything(),
         -starts_with("ResponseId")) %>% 
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("week"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  select(PID,
         TIDnum,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>% # only include variables that vary (i.e., sd != 0)
  as.data.frame 
```

```{r MiS1}
allDuplicated <- function(vec){
  front <- duplicated(vec)
  back <- duplicated(vec, fromLast = TRUE)
  all_dup <- front + back > 0
  return(all_dup)
}

@@

dtMiS1Daily <- dtMiS1Daily %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>% 
  select(
    -any_of(varNamS1Out)
  ) %>%
  select(PID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>% 
  mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  as.data.frame

dtMiS1Weekly <- dtMiS1Weekly %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>% 
  select(
    -any_of(varNamS1Out),
    -ends_with("_calc"),
    -ContactNum,
    -NonDutchNum,
    -keyInteractionTime,
    -InteractionContextCooperative,
    -StudyFeedHonest.post,
    -starts_with("NLE")
  ) %>%
  select(PID,
         TIDnum,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>% 
  mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  as.data.frame

# lares::corr_cross(
#   dtMiS1 %>% select_if(is.numeric), # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 20 # display top 20 couples of variables (by correlation coefficient)
# )
# 
# lares::corr_cross(
#   dtMiS1Daily %>% select_if(is.numeric), # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 20 # display top 20 couples of variables (by correlation coefficient)
# )
# 
# lares::corr_cross(
#   dtMiS1Weekly %>% select_if(is.numeric), # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 20 # display top 20 couples of variables (by correlation coefficient)
# )

# Missingness Percentage
# (colMeans(is.na(dtMiS1Weekly)))*100

#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# MiS1 <-
#   amelia(
#     dtMiS1,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS1, file = "data/imputed/S1Imputed.RData")
load("data/imputed/S1Imputed.RData")

#################################################################
##               Imputation at Daily Aggregation               ##
#################################################################
# MiS1Daily <-
#   amelia(
#     dtMiS1Daily,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS1Daily, file = "data/imputed/S1DailyImputed.RData")
load("data/imputed/S1DailyImputed.RData")

##################################################################
##               Imputation at Weekly Aggregation               ##
##################################################################
# MiS1Weekly <-
#   amelia(
#     dtMiS1Weekly,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS1Weekly, file = "data/imputed/S1WeeklyImputed.RData")
load("data/imputed/S1WeeklyImputed.RData")
```

@@

```{r MiS2}
# BASED ON MiS1
```

@@

>>>>

```{r testOptimizer05}
cleanM <- function(M, c = 55) { #c = 66
  check <- list()
  rowNamesOut <- c()
  colNamesOut <- c()
  for (i in 1:length(c(row.names(M), names(M)))) {
    rowMeans <- rowMeans(M) * 100
    colMeans <- colMeans(M) * 100
    rcMeans <- c(rowMeans, colMeans)
    rm <- which.min(rcMeans) %>% names
    rc <- ifelse(startsWith(rm, "PP_"), "row", "col")

@@

### Main Analysis

We begin by preparing the data for the main analysis, which combines the common variables of all three studies. Here, we:

@@

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiMain <- rbind(
  dtS1Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S1") %>% 
    mutate(across(!TID & !study, as.numeric)),
  dtS2Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S2"),
  dtS3Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S3")
) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(IntergroupContact, IngroupContact, na.rm = TRUE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum)
  ) %>%
  ungroup() %>%
  select(ID,
         study,
         date,
         week,
         everything(),
         -PID,
         -starts_with("ResponseId"), 
         -starts_with("roommate"),
         -starts_with("Reason")) %>%
  as.data.frame %>%
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(ID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  mutate(study = replace_na(study, calc_mode(study))) %>%
  ungroup %>%
  group_by(study, TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>%
  as.data.frame 
```

@@

# # Stability to imputations:
# set.seed(123)
# MiMainStability <-
#   amelia(
#     dtMiMain,
#     m = 20,
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c(
#       "TID",
#       "date",
#       "week",
#       "study",
#       "IntergroupContact",
#       "IngroupContact"
#     ),
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     noms = c("InteractionDum"),
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainStability, file = "data/imputed/MainImputedStability.RData")
load("data/imputed/MainImputedStability.RData")

@@

### Follow-up: Studies

#### Study 1

@@

allDuplicated <- function(vec){
  front <- duplicated(vec)
  back <- duplicated(vec, fromLast = TRUE)
  all_dup <- front + back > 0
  return(all_dup)
}

@@

# lares::corr_cross(
#   dtMiS1 %>% select_if(is.numeric), # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 20 # display top 20 couples of variables (by correlation coefficient)
# )
```

```{r MiS1}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
# set.seed(123)
# MiS1 <-
#   amelia(
#     dtMiS1,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS1, file = "data/imputed/S1Imputed.RData")
load("data/imputed/S1Imputed.RData")

# # Imputation Stability:
# set.seed(123)
# MiS1Stability <-
#   amelia(
#     dtMiS1,
#     m = 20,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS1Stability, file = "data/imputed/S1ImputedStability.RData")
load("data/imputed/S1ImputedStability.RData")
```

#### Study 2

@@

```{r MiS2Prep}
#################################################################
##                    Variable Name Vectors                    ##
#################################################################
varNamS2MiPsbl <- c(
  paste(varNamS2MI, rep(".pre", length(varNamS2MI)), sep = ""),
  varNamS2MI,
  paste(varNamS2MI, rep(".post", length(varNamS2MI)), sep = "")
)

varNamdtS2Noms <- varNames %>%
  filter(
    aux == 1,
    format == "nominal",
    studyS2 == "S2"
  ) %>%
  select(varNam) %>%
  pull

#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiS2 <- dtS2Red %>% 
  select(TID, any_of(varNamS2MiPsbl)) %>% 
  mutate(across(!TID, as.numeric)) %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  select(PID,
         date,
         week,
         everything(),
         -starts_with("ResponseId")) %>%
  as.data.frame %>% 
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., PID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(PID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  ungroup %>% 
  group_by(TIDnum) %>%
  mutate(across(c("date", "week", "TID"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate(across(ends_with(c(".pre", ".post")), ~ ifelse(is.nan(.), NA, .))) %>% 
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         any_of(names(which(sapply(dtMiS2 %>% select(where(is.numeric)), sd, na.rm = TRUE) > 0)))) %>% # only vars that sd != 0
         #which(sapply(. %>% select(where(is.numeric)), sd, na.rm = TRUE) > 0)) %>% # only include variables that vary (i.e., sd != 0)
  as.data.frame

varNamDifS2 <- names(dtMiS2)[gsub(".pre|.post|_calc", "", names(dtMiS2)) %>% allDuplicated]

# # Variables removed for study 2 due to high multicollinearity:
# varNamS1Out <- dtMiS1 %>%
#   select(
#     any_of(varNamDifS1),
#     mdmq.calmness.pre_calc,
#     mdmq.alertness.pre_calc,
#     mdmq.valence.pre_calc,
#     relatednessFrust.pre_calc,
#     competenceFrust.pre_calc,
#     competenceSat.pre_calc,
#     relatednessSat.pre_calc,
#     DutchFriends.pre,
#     secNatDum.pre,
#     timeNL.pre,
#     stress.post,
#     discrimination_month.post,
#     rosenberg.post,
#     qualityStar,
#     starts_with("SSAS")
#   ) %>%
#   names

# dtMiS2Fin <- dtMiS2 %>%
#   # mutate(
#   #   assimilation.dif = assimilation.post - assimilation.pre,
#   #   integration.dif = integration.post - integration.pre,
#   #   marginalization.dif = marginalization.post - marginalization.pre,
#   #   separation.dif = separation.post - separation.pre,
#   #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
#   #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
#   #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
#   #   swl.dif = swl.post_calc - swl.pre_calc
#   # ) %>% 
#   # select(
#   #   -any_of(varNamS2Out)
#   # ) %>%
#   select(PID,
#          TID,
#          TIDnum,
#          date,
#          week,
#          which(sapply(., sd, na.rm = TRUE) > 0)) %>% 
#   mutate_all(~ifelse(is.nan(.), NA, .)) %>%
#   as.data.frame

# lares::corr_cross(
#   dtMiS2 %>% select_if(is.numeric), # name of dataset
#   max_pvalue = 0.05, # display only significant correlations (at 5% level)
#   top = 20 # display top 20 couples of variables (by correlation coefficient)
# )
```

```{r MiS1}
#################################################################
##                     Imputation Bi-daily                     ##
#################################################################
set.seed(123)
MiS2 <-
  amelia(
    dtMiS2,
    m = 1, # 20
    ts = "TIDnum",
    cs = "PID",
    idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
    # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
    # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
    # leads = ...,
    # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
    # parallel = "multicore",
    # ncpus = parallel::detectCores(),
    p2s = 1
  )
save(MiS2, file = "data/imputed/S2Imputed.RData")
load("data/imputed/S2Imputed.RData")

# # Imputation Stability:
# set.seed(123)
# MiS1Stability <-
#   amelia(
#     dtMiS1,
#     m = 20,
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week", "IntergroupContact", "IngroupContact"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS1Stability, file = "data/imputed/S1ImputedStability.RData")
load("data/imputed/S1ImputedStability.RData")
```

#### Study 3

@@

### Follow-up: Time Scales

#### Daily

Preparing the data for the time scale follow-up, which combines the common variables of all three studies on a daily level. Here, we:

```{r MiDailyPrep}
#################################################################
##                    Dataframe Preparation                    ##
#################################################################
dtMiMainDaily <- rbind(
  dtS1Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S1") %>% 
    mutate(across(!TID & !study, as.numeric)),
  dtS2Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S2"),
  dtS3Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S3")
) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(IntergroupContact, IngroupContact, na.rm = TRUE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum)
  ) %>%
  ungroup() %>%
  group_by(ID, date, study) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>% # contact dum should be summarized as sum()
  ungroup %>%
  group_by(study) %>%
  mutate(TIDnum = as.numeric(factor(date))) %>%
  ungroup %>%
  select(ID,
         study,
         date,
         everything(),
         -PID,
         -starts_with("ResponseId")) %>%
  as.data.frame %>%
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(ID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  mutate(study = replace_na(study, calc_mode(study))) %>%
  ungroup %>%
  group_by(study, TIDnum) %>%
  mutate(across(c("date"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate_if(is.numeric, ~ ifelse(is.nan(.), NA, .)) %>%
  as.data.frame 
```

```{r DailyImp}
#################################################################
##               Imputation at Daily Aggregation               ##
#################################################################
# MiMainDaily <-
#   amelia(
#     dtMiMainDaily,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("date", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMainDaily)[!names(dtMiMainDaily) %in% idVars],
#     #lags = names(dtMiMainDaily)[names(dtMiMainDaily) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainDaily)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainDaily))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainDaily, file = "data/imputed/MainDailyImputed.RData")
load("data/imputed/MainDailyImputed.RData")

# # Stability to imputations:
# set.seed(123)
# MiMainDailyStability <-
#   amelia(
#     dtMiMainDaily,
#     m = 20,
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("date", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMainDaily)[!names(dtMiMainDaily) %in% idVars],
#     #lags = names(dtMiMainDaily)[names(dtMiMainDaily) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainDaily)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainDaily))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainDailyStability, file = "data/imputed/MainDailyImputedStability.RData")
load("data/imputed/MainDailyImputedStability.RData")
```

#### Weekly

Preparing the data for the time scale follow-up, which combines the common variables of all three studies on a weekly level. Here, we:

```{r MiWeeklyPrep}
dtMiMainWeeekly <- rbind(
  dtS1Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S1") %>% 
    mutate(across(!TID & !study, as.numeric)),
  dtS2Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S2"),
  dtS3Red %>% select(any_of(varNamS123MiRed)) %>% mutate(study = "S3")
) %>%
  group_by(study, PID) %>%
  mutate(ID = cur_group_id()) %>%
  ungroup %>%
  mutate(
    date = as.Date(gsub(" .*", "", TID)),
    week = strftime(date, format = "%Y-W%V")
  ) %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(IntergroupContact, IngroupContact, na.rm = TRUE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum)
  ) %>%
  ungroup() %>%
  group_by(ID, week, study) %>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ungroup %>%
  group_by(study) %>%
  mutate(TIDnum = as.numeric(factor(week))) %>%
  ungroup %>%
  select(ID,
         study,
         week,
         everything(),
         -PID,
         -starts_with("ResponseId")) %>%
  as.data.frame %>%
  select_if(~ sum(!is.na(.)) > 1) %>% # only include variables that have any data (i.e., not all NA)
  complete(., ID, TIDnum) %>% # add na if id and TID combination is missing
  group_by(ID) %>%
  mutate(across(ends_with(c(".pre", ".post")),  ~ replace_na(.x, mean(.x, na.rm = TRUE)))) %>%
  mutate(study = replace_na(study, calc_mode(study))) %>%
  ungroup %>%
  group_by(study, TIDnum) %>%
  mutate(across(c("week"),  ~ replace_na(.x, calc_mode(.x)))) %>%
  ungroup %>% 
  mutate_if(is.numeric, ~ ifelse(is.nan(.), NA, .)) %>%
  as.data.frame 
```

```{r WeeklyImp}
##################################################################
##               Imputation at Weekly Aggregation               ##
##################################################################
# MiMainWeekly <-
#   amelia(
#     dtMiMainWeeekly,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("week", "study", "IntergroupContact", "IngroupContact"), #"PID",
#     #lags = names(dtMiMainWeeekly)[!names(dtMiMainWeeekly) %in% idVars],
#     #lags = names(dtMiMainWeeekly)[names(dtMiMainWeeekly) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainWeeekly)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainWeeekly))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainWeekly, file = "data/imputed/MainWeeklyImputed.RData")
load("data/imputed/MainWeeklyImputed.RData")
